High-Dimensional Regularized Discriminant Analysis

### 2017-10-17 reports/paper-hdrda.Rnw
added word count for journal
Added TIFF format because JSCS. :(

@@

% TODO:
% 1. Word count
% 2. Update plots to TIFF format with correct parameters.
% 3. Are MSC codes needed?: \MSC[2010] 62H30\sep 65F15\sep 65F20\sep 65F22

@@

opts_chunk$set(fig.align='default', dev='png', message=FALSE, warning=FALSE,
               cache=TRUE, echo=FALSE, autodep=TRUE, fig.width=12,
               fig.height=12, out.width="\\linewidth")
@

@@

\begin{figure}
<<hdrda_contours, fig.width=8, fig.height=8, out.width='.33\\linewidth', dpi=200, fig.show='hold'>>=
rda_contours(lambda = 0)
rda_contours(lambda = 0.2)
rda_contours(lambda = 0.4)
rda_contours(lambda = 0.6)
rda_contours(lambda = 0.8)
rda_contours(lambda = 1)
@
\caption{Contours of five multivariate normal populations as a function of the
  pooling parameter $\lambda$.}
\label{fig:hdrda-contours}
\end{figure}

@@

\begin{figure}
<<timing_results, fig.width=8, fig.height=8, dpi=200>>=
p <- ggplot(timings_combined, aes(x=p, y=time, color=Classifier))
p <- p + geom_point() + geom_jitter(width=140, height=0) + facet_wrap(~ Plot, scales="free_y")
p <- p + geom_smooth(method="lm", formula=y ~ poly(x, 2), se=FALSE)
p <- p + scale_color_manual(values=c("#D55E00", "#0072B2"))
p <- p + xlab("Number of Features") + ylab("Model Selection Time (seconds)")
p + theme_bw()
@
\caption{Timing comparisons (in seconds) between HDRDA and RDA classifiers.}
\label{fig:timing-results}
\end{figure}

@@

\begin{figure}
<<relative_timings, fig.width=8, fig.height=8, dpi=200>>=
p <- ggplot(timing_ratios_bootstrap, aes(ratio_means, fill=p))
p <- p + geom_histogram() + facet_wrap(~ p, scale="free_x")
p <- p + xlab("Ratio of Mean RDA Runtime to Mean HDRDA Runtime") + ylab("Bootstrap Replications")
p + theme_bw()
@
\caption{Distribution of ratios of mean \emph{RDA} runtime to mean \emph{HDRDA}
  runtime across 1000 bootstrap replications.}
\label{fig:timing-comparison-bootstrap}
\end{figure}

@@

\begin{figure}
<<sim_results, fig.width=8, fig.height=8, dpi=200>>=
p <- ggplot(results_contaminated, aes(x=contamination_prob, y=Error))
p <- p + geom_line(aes(color=Classifier, linetype=Classifier), size=0.65)
p <- p + facet_wrap(~ p, labeller = "label_both")
p <- p + xlab("Contamination Probability") + ylab("Average Error Rate")
p + theme_bw()
@
\caption{Average classification error rates as a function of the contamination
  probability $\epsilon$. Approximate standard errors were no greater than
  \Sexpr{max_sim_se}.}
\label{fig:sim-results}
\end{figure}

@@

\begin{figure}
<<sim_results_by_p, fig.width=8, fig.height=8, dpi=200>>=
p2 <- results_contaminated %>%
  mutate(p=as.numeric(as.character(p)),
         contamination_prob=round(contamination_prob, digits=2)) %>%
    filter(contamination_prob %in% c(0.0, 0.1, 0.2, 0.3, 0.4, 0.5)) %>%
    rename(`Contamination Probability`=contamination_prob) %>%
      ggplot(., aes(x=p, y=Error))
p2 <- p2 + geom_line(aes(color=Classifier, linetype=Classifier), size=0.65)
p2 <- p2 + facet_wrap(~ `Contamination Probability`, labeller="label_both")
p2 <- p2 + xlab("Number of Features") + ylab("Average Error Rate")
p2 + theme_bw()
@
\caption{Average classification error rates as a function of the number of
  features $p$. Approximate standard errors were no greater than
  \Sexpr{max_sim_se}.}
\label{fig:sim-results-by-p}
\end{figure}

>>>>

% Word Count for journal: 7,059
% detex paper-hdrda.tex | wc -w

@@

% TODO: Are MSC codes needed?: \MSC[2010] 62H30\sep 65F15\sep 65F20\sep 65F22

@@

opts_chunk$set(fig.align='default', dev=c("tiff", "png"),
               message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE, autodep=TRUE,
               dpi=300, fig.width=12, fig.height=12, out.width="\\linewidth")
@

@@

\begin{figure}
<<hdrda_contours, fig.width=8, fig.height=8, out.width='.33\\linewidth', fig.show='hold'>>=
rda_contours(lambda = 0)
rda_contours(lambda = 0.2)
rda_contours(lambda = 0.4)
rda_contours(lambda = 0.6)
rda_contours(lambda = 0.8)
rda_contours(lambda = 1)
@
\caption{Contours of five multivariate normal populations as a function of the
  pooling parameter $\lambda$.}
\label{fig:hdrda-contours}
\end{figure}

@@

\begin{figure}
<<timing_results, fig.width=8, fig.height=8>>=
p <- ggplot(timings_combined, aes(x=p, y=time, color=Classifier))
p <- p + geom_point() + geom_jitter(width=140, height=0) + facet_wrap(~ Plot, scales="free_y")
p <- p + geom_smooth(method="lm", formula=y ~ poly(x, 2), se=FALSE)
p <- p + scale_color_manual(values=c("#D55E00", "#0072B2"))
p <- p + xlab("Number of Features") + ylab("Model Selection Time (seconds)")
p + theme_bw()
@
\caption{Timing comparisons (in seconds) between HDRDA and RDA classifiers.}
\label{fig:timing-results}
\end{figure}

@@

\begin{figure}
<<relative_timings, fig.width=8, fig.height=8>>=
p <- ggplot(timing_ratios_bootstrap, aes(ratio_means, fill=p))
p <- p + geom_histogram() + facet_wrap(~ p, scale="free_x", labeller="label_both")
p <- p + xlab("Ratio of Mean RDA Runtime to Mean HDRDA Runtime") + ylab("Bootstrap Replications")
p + theme_bw()
@
\caption{Distribution of ratios of mean \emph{RDA} runtime to mean \emph{HDRDA}
  runtime across 1000 bootstrap replications.}
\label{fig:timing-comparison-bootstrap}
\end{figure}

@@

\begin{figure}
<<sim_results, fig.width=8, fig.height=8>>=
p <- ggplot(results_contaminated, aes(x=contamination_prob, y=Error))
p <- p + geom_line(aes(color=Classifier, linetype=Classifier), size=0.65)
p <- p + facet_wrap(~ p, labeller = "label_both")
p <- p + xlab("Contamination Probability") + ylab("Average Error Rate")
p + theme_bw()
@
\caption{Average classification error rates as a function of the contamination
  probability $\epsilon$. Approximate standard errors were no greater than
  \Sexpr{max_sim_se}.}
\label{fig:sim-results}
\end{figure}

@@

\begin{figure}
<<sim_results_by_p, fig.width=8, fig.height=8>>=
p2 <- results_contaminated %>%
  mutate(p=as.numeric(as.character(p)),
         contamination_prob=round(contamination_prob, digits=2)) %>%
    filter(contamination_prob %in% c(0.0, 0.1, 0.2, 0.3, 0.4, 0.5)) %>%
    rename(`Contamination Probability`=contamination_prob) %>%
      ggplot(., aes(x=p, y=Error))
p2 <- p2 + geom_line(aes(color=Classifier, linetype=Classifier), size=0.65)
p2 <- p2 + facet_wrap(~ `Contamination Probability`, labeller="label_both")
p2 <- p2 + xlab("Number of Features") + ylab("Average Error Rate")
p2 + theme_bw()
@
\caption{Average classification error rates as a function of the number of
  features $p$. Approximate standard errors were no greater than
  \Sexpr{max_sim_se}.}
\label{fig:sim-results-by-p}
\end{figure}
